---
title: Guide to Using and Installing 'ggplot2'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Getting Started

Download [R](https://www.r-project.org/about.html) and [RStudio](https://rstudio.com/products/rstudio/download/) for using R much better!

The following steps and tutorials are implemented in RStudio.

***

## Installation and Usage

```{r eval=FALSE}
# The easiest way to get ggplot2 is to install the whole tidyverse:
install.packages("tidyverse")

# Alternatively, install just ggplot2:
install.packages("ggplot2")

# Or the development version from GitHub:
# install.packages("devtools")
devtools::install_github("tidyverse/ggplot2")
```

To use ggplot2 in your workspace, include in your code:

```{r eval=FALSE}
library(ggplot2)
```

Source [here](https://ggplot2.tidyverse.org/).

***

## Tutorials

* [Basic Tutorial](http://r-statistics.co/ggplot2-Tutorial-With-R.html)
* [Advanced Tutorial](http://r-statistics.co/Complete-Ggplot2-Tutorial-Part1-With-R-Code.html)
* [Customizing Plots](http://r-statistics.co/Complete-Ggplot2-Tutorial-Part2-Customizing-Theme-With-R-Code.html)
* [Top 50 ggplot2 Visualizations](http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html)

After reading the first three tutorials, try completing [this](https://sohumdatta.github.io/pcari-sp20/handouts/Exercises2_handout1.html) exercise including the challenge to become more familiar with ggplot2. Have fun!
