---
title: "Configuring Ubuntu Virtual Machine"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The package **pacman** is very useful for installing packages instantly. However, this package is only available for R 3.4-3.6. To install R 3.6.3:

```{r eval=FALSE}
sudo add-apt-repository 'deb https://cloud.r-project.org/bin/linux/ubuntu xenial-cran35/'
sudo apt-key adv --keyserver keyserver.ubuntu.com --recv-keys E298A3A825C0D65DFD57CBB651716619E084DAB9
sudo apt update
sudo apt install r-base
```

Then, download the latest version of [RStudio](https://rstudio.com/products/rstudio/download/) for your version of Ubuntu. Then install gdebi to unpack the RStudio installer:

```{r eval=FALSE}
sudo apt-get install gdebi-core
```

Go to the folder where you downloaded the installer and open the terminal from there.

```{r eval=FALSE}
sudo dpkg -i <name of installer>
```

To install pacman:

```{r eval=FALSE}
install.packages("pacman")
```

Next, you need the libraries **ggplot2** and **rmarkdown**. To install these, just type in the RStduio console:

```{r eval=FALSE}
pacman::p_load(ggplot2, rmarkdown)
```

Other libraries that you want to install can be installed like this later. Additionally, you need to do this step to be able to export your Rmd files as PDFs:

```{r eval=FALSE}
tidyverse::tiny_latex()
```

If there is an error, see the R Markdown tab from RStudio to check the right command. It should be at the last part of the message. You can also try installing the **latexpdf** or **pdflatex** package.